---
title: "Quality Prediction of Barbell Lift Exercises"
author: "yx"
date: "February 27, 2016"
output: html_document
---

## Introduction

The goal of this project is to develop a model to predict the quality of barbell lift exercises based on the data of Weight Lifting Exercise Dataset. 

## Data Import and Processing

As the first step of this project, the Weight Lifting Exercise training and testing dataset were imported. The variables without variability or mostly missing were removed based on a close examination of the training and testing data. Only the useful features were extracted and used in the later analysis.

```{r, echo=TRUE, cache=TRUE}
raw_training<-read.csv("./pml-training.csv")
raw_testing<-read.csv("./pml-testing.csv")

myvars1 <- grepl( "^kurtosis", names(raw_training)) | grepl( "^max", names(raw_training)) | grepl( "^min", names(raw_training)) | grepl( "^skewness", names(raw_training)) | grepl( "^amplitude", names(raw_training)) | grepl( "^var", names(raw_training)) | grepl( "^avg", names(raw_training)) | grepl( "^stddev", names(raw_training)) | grepl( "^user", names(raw_training)) | grepl( "^cvtd", names(raw_training)) | grepl( "X", names(raw_training)) | grepl( "^raw", names(raw_training)) | grepl( "new_window", names(raw_training))
training <- raw_training[!myvars1]

myvars2 <- grepl( "^kurtosis", names(raw_testing)) | grepl( "^max", names(raw_testing)) | grepl( "^min", names(raw_testing)) | grepl( "^skewness", names(raw_testing)) | grepl( "^amplitude", names(raw_testing)) | grepl( "^var", names(raw_testing)) | grepl( "^avg", names(raw_testing)) | grepl( "^stddev", names(raw_testing)) | grepl( "^user", names(raw_testing)) | grepl( "^cvtd", names(raw_testing)) | grepl( "X", names(raw_testing)) | grepl( "problem_id", names(raw_testing)) | grepl( "^raw", names(raw_testing)) | grepl( "new_window", names(raw_testing))
testing <- raw_testing[!myvars2]
```

## Prediction Model Development

In this project, random forest method combined with 5-fold cross validation was applied to construct the prediction model. The reason to select random forest method as it can do feature selection. 

```{r, echo=TRUE, cache=TRUE, warning=FALSE}
library(caret)
library(doParallel)

fitControl<-trainControl(method="cv", number=5)

c1<-makeCluster(detectCores())
registerDoParallel(c1)

set.seed(1234)
modFit1<-train(classe~., method="rf", data=training, trControl=fitControl, metric="Kappa",importance=TRUE)

stopCluster(c1)

print(modFit1)

# Final model
print(modFit1$finalModel)
confusionMatrix(predict(modFit1,training), training$classe)

# Prediction on test data
predict(modFit1,testing)
```

As shown in the above final model, the accuracy of developed model based on the training data is about 99.8%.
